# Installation {#intro}

Like GeoDa desktop software, rgeoda are avaiable to different platforms including: Mac, Linux and Windows. 


## Mac

In R console, use install.packages() function to install rgeoda from its **binary pacakge**: 

```r
install.packages("https://github.com/lixun910/rgeoda/releases/download/0.0.3/rgeoda_0.0.3_osx.tgz")
```

If you have an older version of Mac OS and the above command failed to install rgeoda, please try to install "Xcode Command Line Tools" and then install rgeoda from source:
```r
install.packages("https://github.com/lixun910/rgeoda/releases/download/0.0.3/rgeoda_0.0.3.tar.gz")
# or the development version
# devtools::install_github("lixun910/rgeoda")
```

## Linux

In R console, use install.packages() function to install rgeoda from its **source pacakge**: 

```r
install.packages("https://github.com/lixun910/rgeoda/releases/download/0.0.3/rgeoda_0.0.3.tar.gz")
# or the development version
# devtools::install_github("lixun910/rgeoda")
```

## Windows

In R console, one can use install.packages() function to install rgeoda from its **binary pacakge**: 

```{r eval=FALSE}
install.packages("https://github.com/lixun910/rgeoda/releases/download/0.0.3/rgeoda_0.0.3.zip")
# or the development version
# devtools::install_github("lixun910/rgeoda")
```

```{block, type='rmdwarn'}
Install rgeoda on windows from source package is not recommended. You would try if you know how to deal with [R devtools](https://www.r-project.org/nosvn/pandoc/devtools.html) on windows.
```

## Load rgeoda library in R

If everything installed without error, you should be able to load rgeoda:


```{r}
library(rgeoda)
```

```{block, type='rmdinfo'}
We are working to make rgeoda avaiable in CRAN, so that it could be installed easily (target in 0.1.0 version).
```
