# Installation {#intro}

Like GeoDa desktop software, rgeoda are avaiable to different platforms including: Mac, Linux and Windows. 

## Dependencies

rgeoda depends on `wkb` package. Sometimes, the "dependencies=TRUE" argument of `install.package()` doesn't guarantee the installation ow `wkb` automatically. To avoid any potential issues of installation, you can install it first before rgeoda installation:

```r
install.packages(wkb)
```

## Mac

For Mac users, the "Xcode Command Line Tools" needs to be installed for installing rgeoda. It is a free software provided by Apple, which can be installed by using the following command in a terminal:
```
xcode-select --install 
```

In R console, use install.packages() function to install rgeoda from its **source pacakge**: 
```r
install.packages("https://github.com/lixun910/rgeoda/releases/download/0.0.3/rgeoda_0.0.3.tar.gz", dependencies=c('wkb'))
# or the development version
# devtools::install_github("lixun910/rgeoda")
```

## Windows

In R console, one can use install.packages() function to install rgeoda from its **binary pacakge**: 

```{r eval=FALSE}
install.packages("https://github.com/lixun910/rgeoda/releases/download/0.0.3/rgeoda_0.0.3.zip", dependencies=c('wkb'))
```

```{block, type='rmdwarn'}
Install rgeoda on windows from source package is not recommended. You would try if you know how to deal with [R devtools](https://www.r-project.org/nosvn/pandoc/devtools.html) on windows.
```

## Linux

For Linux users, the "Build Essential Tools" needs to be installed first:
```
sudo apt-get update
sudo apt-get install build-essential
```

Then, in R console, use install.packages() function to install rgeoda from its **source pacakge**: 

```r
install.packages("https://github.com/lixun910/rgeoda/releases/download/0.0.3/rgeoda_0.0.3.tar.gz", dependencies=c('wkb'))
# or the development version
# devtools::install_github("lixun910/rgeoda")
```


## Load rgeoda library in R

If everything installed without error, you should be able to load rgeoda:


```{r}
library(rgeoda)
```

```{block, type='rmdinfo'}
We are working to make rgeoda avaiable in CRAN, so that it could be installed easily (target in 0.1.0 version).
```
