# Load Spatial Data

The data formats that rgeoda v0.0.3 can load directly includes: 

* ESRI Shapefile
* MapInfo File
* CSV
* GML
* GPX 
* KML
* GeoJSON
* TopoJSON
* OpenFileGDB
* GFT Google Fusion Tables
* CouchDB 

Note: in this tutorial, we only tested loading ESRI shapefiles using rgeoda v0.0.3. Please create a ticket in rgeoda's [repository](https://github.com/lixun910/rgeoda/issues) if you experience any issues when loading spatial data. 

For example, to load the ESRI Shapefile `Guerry.shp` (source: https://geodacenter.github.io/data-and-lab/Guerry/) comes with the package:

```{r echo=TRUE}
guerry_path <- system.file("extdata", "Guerry.shp", package = "rgeoda")
guerry <- geoda_open(guerry_path)
```

The `geoda_open` function returns a geoda object, which can be used to access the meta-data, fields, and columns of the input dataset.

```
Usage
geoda_open(ds_path)

Arguments
ds_path	(character) The path of the spatial dataset

Value
gda_obj An object of geoda class
```

## Attributes of `geoda` object

* n_cols
* n_obs
* field_names
* field_types
* table (data.frame)

To access the meta-data of the loaded Guerry dataset:
```{r}
cat("\nnumber of columns:", guerry$n_cols)
cat("\nnumber of observations:", guerry$n_obs)
cat("\nfield names:", guerry$field_names)
cat("\nfield types:", guerry$field_types)
```

## Access Table Data

The geoda instance has a R data.frame attribute `table`, which stores the data loaded from the dataset:

```{r}
guerry$table
```

With the `table` attribute, we can, for example, get the values of "Crm_prp" column:

```{r}
crm_prp <- guerry$table$Crm_prp
cat("\nfirs 10 values of Crm_prp:", crm_prp[1:10])
```


