# Spatial Weights

Spatial weights are central components in spatial data analysis. The spatial weights represents the possible spatial interaction between observations in space. Like GeoDa desktop software, `rgeoda` provides a rich variety of methods to create several different types of spatial weights:

* Contiguity Based Weights: `queen_weights()`, `rook_weights()`
* Distance Based Weights: `distance_weights()`
* K-Nearest Neighbor Weights: `knn_weights()`
* Kernel Weights: `distance_weights()` and `knn_weights()` with kernel parameters

## Queen Contiguity Weights

To create a Queen contiguity weights, we can call pygeoda's function 
```r
gda_queen(gda, order=1, include_lower_order = False, precision_threshold = 0)
``` 
by passing the GeoDa object `guerry` we just created: 

```{r}
queen_w <- queen_weights(guerry)
queen_w
```

The function `queen_weights()` returns an instance of 
`Weight` object. One can access the meta data of the spatial
weights by accessing the attributes of `GeoDaWeight` object:

## Attributes of `Weight` object

* weight_type
* is_symmetric
* sparsity
* density
* min_nbrs
* max_nbrs
* mean_nbrs
* median_nbrs
* bool HasIsolates()
* [] GetNeighbors(idx)
* double SpatialLag(idx, [data])
* SaveToFile()

We can also access the details of the weights: e.g. list the neighbors of a specified observation, which is very helpful in exploratory spatial data analysis (which is focused in next tutorial):

```{r}
nbrs <- queen_w$GetNeighbors(0)
cat("\nNeighbors of 0-st observation are:", nbrs)
```
We can also compute the spatial lag of a specified observation by passing the values of the selected variable:

```{r}
lag0 <- queen_w$SpatialLag(0, crm_prp)
cat("\nSpatial lag of 0-st observation is:", lag0)
```

## Rook Contiguity Weights

To create a Rook contiguity weights, we can call pygeoda's function 
```r
rook_weights(gda, order=1,include_lower_order=False, precision_threshold = 0)
``` 
by passing the GeoDa object `guerry` we just created: 

```{r}
rook_w <- rook_weights(guerry)
rook_w
```

The weights we created are in memory, which makes it straight forward for spatial data analysis and also are good for programming your application. To save the weights to a file, we need to call GeoDaWeight's function 
```r
SaveToFile(ofname, layer_name, id_name, id_vec)
```

The `layer_name` is the layer name of loaded dataset. For a ESRI shapefile, the layer name is the file name without the suffix (e.g. Guerry). 

The `id_name` is a key (column name), which means the associated column contains unique values, that makes sure that the weights are connected to the correct observations in the data table. 

The `id_vec` is the actual column data of `id_name`, it could be a tuple of integer or string values.

For example, in Guerry dataset, the column "CODE_DE" can be used as a key to save a weights file:

```{r}
rook_w$SaveToFile('/Users/xun/Downloads/Guerry_r.gal', 'Guerry', 'CODE_DE', guerry$GetIntegerCol('CODE_DE'))
```

Then, we should find the file "Guerry_r.gal" in the output directory.

## Distance Based Weights

To create a Distance based weights, we can call rgeoda's function 
```r
gda_distance_weights(gda, dist_thres, power=1.0,  is_inverse=False, is_arc=False, is_mile=True)
``` 
by passing the GeoDa object `guerry` we just created and the value of distance threshold. Like GeoDa, rgeoda provides a function to help you find a optimized distance threshold that guarantees that every observation has at least one neighbor:

```r
gda_min_distthreshold(GeoDa gda, bool is_arc = False, bool is_mile = True)
```

```{r}
dist_thres <- min_distthreshold(guerry)
dist_w <- distance_weights(guerry, dist_thres)
dist_w
```
## K-Nearest Neighbor Weights

A special case of distance based weights is K-Nearest neighbor weights, in which every obersvation will have exactly k neighbors. To create a KNN weights, we can call pygeoda's function:
```r
gda_knn_weights(gda, k, power = 1.0,is_inverse = False, is_arc = False, is_mile = True)
```

For example, to create a 6-nearest neighbor weights using Guerry dataset:
```{r}
knn6_w <- knn_weights(guerry, 6)
knn6_w
```

## Kernel Weights

Kernel weights apply kernel function to determine the distance decay in the derived continuous weights kernel. The kernel weights are defined as a function K(z) of the ratio between the distance dij from i to j, and the bandwidth hi, with z=dij/hi. 

The kernl functions include

* triangular
* uniform 
* quadratic
* epanechnikov
* quartic
* gaussian

Two functions are provided in rgeoda to create kernel weights:

### Kernel Weights with fixed bandwidth

To create a kernel weights with fixed bandwith:
```{r}
bandwidth <- min_distthreshold(guerry)
kernel_w <- kernel_weights(guerry, bandwidth, "uniform")
kernel_w
```

Besides the options `is_inverse`, `power`, `is_arc` and `is_mile` that are the same with the distance based weights, this kernel weights function has another option:
```
use_kernel_diagonals	
(optional) FALSE (default) or TRUE, apply kernel on the diagonal of weights matrix
```

### Kernel Weights with adaptive bandwidth

To create a kernel weights with adaptive bandwidth or using max KNN distance as bandwidth:
```{r}
adptkernel_w = kernel_knn_weights(guerry, 6, "uniform")

adptkernel_w
```

This kernel weights function two more options:
```
adaptive_bandwidth	
(optional) TRUE (default) or FALSE: TRUE use adaptive bandwidth calculated using distance of k-nearest neithbors, FALSE use max distance of all observation to their k-nearest neighbors

use_kernel_diagonals	
(optional) FALSE (default) or TRUE, apply kernel on the diagonal of weights matrix
```
